---
title: "Title goes here"
author: "[Vijay Lulla](https://vlulla.github.io/)"
date: "`r strftime(Sys.Date(), format='%Y.%m.%d')`"
output:
  html_document:
    number_sections: true
    fig_caption: true
    code_folding: hide
  pdf_document:
    keep_tex: false
    number_sections: true
  word_document:
    fig_caption: true
documentclass: scrartcl
fontfamily: libertinus
fontfamilyoptions:
- osf
- p
fontsize: 11pt
microtypeoptions:
- final
- tracking=true
- kerning=true
- spacing=true
- factor=1100
- stretch=10
- shrink=10
lot: true
lof: true

geometry: margin=1in
bibliography: mybibliography.bib
csl: apa.csl
---


```{r global_options, echo=FALSE, include=FALSE}
knitr::opts_knit$set(progress=FALSE, verbose=TRUE)
knitr::opts_chunk$set(echo=TRUE, collapse=TRUE, message=FALSE, warning=FALSE, dpi=150, fig.width=8, fig.height=6, fig.path="figs/")
```

# Introduction {#intro}

Write your introduction here!

It is usually multiple paragraphs.

# Literature Review (or background) {#background}

Write your background/literature review here!  You'll need to include citations
in your report.  Here's how to do citation [@bogar_green_space_2016].  And,
@farris_creation_2009 is the way to cite inline!

# Data and methods {#data-and-methods}

Since this is a report containing R snippets it will include stuff for R code
along with the descriptions of the data that you need.  Please also include
where you got the data from!

## Libraries {#libraries}

```{r, message=FALSE}
library(data.table)
library(magrittr)
library(sf)
library(raster)
library(ggplot2)

```


## Data Description {#data-description}

More description of the data if required.

# Results {#results}

Discuss your results here.  Instead of describing the tables and/or figures try
to explain how to interpret what we're seeing in the tables, figures, and
charts.

```{r, fig.cap="My first figure"}
with(mtcars, plot(mpg, drat, xlab="Miles/gallon", ylab="Rear axle drag ratio", pch=20))
```

# Discussions {#discussion}

Discuss anything that doesn't fit anywhere else!


Here are some miscellaneous notes:

<https://www.google.com> link directly!

[Google](https://www.google.com) link with separate content for link and href!

To show a code block indent by **four spaces**.  Let's see if it works

    randstr <- function(length=10) {
      paste0(sample(c(letters, LETTERS), length, replace=TRUE), collapse="")
    }
    set.seed(1234L)
    randstr()

Let's see if this actually works!

```{r, echo=TRUE}
randstr <- function(length=10) {
  paste0(sample(c(letters, LETTERS), length, replace=TRUE), collapse="")
}
set.seed(1234L)
randstr()
```

To include  a list just create a correctly aligned bullet-list like so:

* item 1
* item 2
* **bold item 3**
* 3 * 2 + 5 = `r 3 * 2 + 5`

And here's an example of block quote:

> I returned and saw under the sun, that the race is not to the swift, nor the
> battle to the strong, neither yet bread to the wise, nor yet riches to men of
> understanding, nor yet favour to men of skill; but time and chance happenth to
> them all.
>
> --- In George Orwell's _Politics and the English Language_
> [Link](http://www.orwell.ru/library/essays/politics/english/e_polit)

The end!

# References {#references}
